---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(rmarkdown)
library(readr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(hrbrthemes)
library(plotly)
library(gridExtra)
library(dplyr)
library(COVID19CHN)
```

# COVID19CHN

<!-- badges: start -->
[![R build status](https://github.com/etc5523-2020/r-package-assessment-Lulu-Pi/workflows/R-CMD-check/badge.svg)](https://github.com/etc5523-2020/r-package-assessment-Lulu-Pi/actions)
<!-- badges: end -->

The goal of COVID19CHN is to help launching the shiny app with datasets and functions, which helps with basic analysis of COVID-19 daily cases of every province in China, including confirmed cases, death cases and recovered cases as of 30 September 2020.  

## Installation

You can install the development version of COVID19CHN from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-Lulu-Pi")
```

## Example

This is a basic example which shows you what the package includes: 

### The dataset of COVID-19 daily cases in each province in China
```{r tibble, echo = FALSE, warning = FALSE, message=FALSE}
library(tibble)
tibble(China_covid19)
```

### The COVID-19 cases per month from January in China
```{r example, echo = FALSE, warning = FALSE, message=FALSE}
library(kableExtra)
China_covid19 %>%
  select(-Lat, -Long, -Date) %>%
  group_by(Month,
          `Province/State`) %>%
  summarise(Confirmed = sum(Confirmed),
            Deaths = sum(Deaths),
            Recovered = sum(Recovered, na.rm = TRUE)) %>%
  head(10) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```


### COVID19 daily cases trend in some provinces or states China
```{r line_example, echo = FALSE, warning = FALSE, message=FALSE}
China_covid19 %>% 
  filter(`Province/State` %in% c("Shanghai", "Beijing", "Guangdong")) %>%
  pivot_longer(cols = c("Confirmed",
                      "Deaths",
                      "Recovered"),
             names_to = "Type",
             values_to = "Cases") %>% 
  group_by(Date, Type, `Province/State`) %>% 
  summarise(Cases = sum(Cases, na.rm = TRUE)) %>%
  ggplot(aes(x = Date, y = Cases, color = Type)) +
  geom_line() +
  facet_wrap(~`Province/State`, ncol = 1) +
  theme_bw()
  
  

```
 

